Enforced Invariant Confluence

### 2018-03-04 doc/paper_redux/interactive_decision_procedure.tex
Illustrated example interaction.

Let's walk through how we might use \IsIconfluent{} on
\exampleref{StateBasedNotNecessary}.
\begin{itemize}
  \item
    \IsIconfluent{} calls \Helper{} with $R = \set{(0, 0)}, NR = \emptyset{}$.

  \item
    \Helper{} determines that $O$ is not \iclosed{$(I - R)$} with
    counterexample $s_1 = (-1, 1)$ and $s_2 = (1, -1)$. We take the third
    branch.

  \item
    We randomly generate some reachable points and update $R$ to $\set{(0, 0),
    (1, 0), (0, -1), (1, -1)}$. Lucky for us, $s_2 \in R$, so we know it is
    reachable. We're not sure about $s_1$, so we ask the user. After some
    thought, the user tells us that $s_1$ is unreachable. We recurse with $R =
    \set{(0, 0), (1, 0), (0, -1), (1, -1)}$ and $NR = \set{(-1, 1)}$.

  \item
    \Helper{} determines that $O$ is not \iclosed{$(I - R)$} with
    counterexample $s_1 = (-1, 2)$ and $s_2 = (10, -10)$. We take the third
    branch.

  \item
    We randomly generate some more reachable points and update $R$ to $\set{(0,
    0), (1, 0), (0, -1), (1, -1), (2, 0), (0, -2)}$. $s_1, s_2 \notin R, NR$,
    so we ask the user to label them. The user puts $s_1$ in $NR$ and $s_2$ in
    $R$. We recurse with $R = \set{(0, 0), (1, 0), (0, -1), (1, -1), (2, 0),
    (0, -2), (10, -10)}$ and $NR = \set{(-1, 1), (-1, 2)}$.

  \item
    \Helper{} determines that $O$ is not \iclosed{$(I - R)$} with
    counterexample $s_1 = (-2, 1)$ and $s_2 = (4, -3)$. We take the third
    branch.

  \item
    We randomly generate some more reachable points and update $R$. $s_1, s_2
    \notin R, NR$, so we ask the user to label them. The user notices a pattern
    in $R$ and $NR$ and after some thought, concludes that every point with
    negative $x$-coordinate is unreachable. They update $NR$ to $-\ints \times
    \ints$. We recurse.

  \item
    \Helper{} determines that $O$ is \iclosed{$(I - R)$} and returns yes!
\end{itemize}

\todo{What if the user labels things incorrectly?}

>>>>

An example of how to use \algoref{InteractiveDecisionProcedure} on
\exampleref{StateBasedNotNecessary} is given in
\figref{DecisionProcedureExample}.

\input{figs/decision_procedure_example.fig}

\todo{Describe what happens when user input is incorrect.}
